A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-23 paper.tex
general n

The dimensional reduction of 8d $\cN=1$ super Yang--Mills on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is by definition the $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 16 supercharges. Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\U(1)\times \Spin(N_\RR)$. We consider the grading $\alpha\colon \U(1)\rightarrow G_\RR$ given by the embedding into the first copy of $\U(1)$ and a twisting homomorphism
\[\phi\colon \MU(L)\times \Spin(N_\RR)\xrightarrow{\det^{1/2}\times \id} G_R=\U(1)\times \Spin(N_\RR).\]

@@

The dimensional reduction of 6d super Yang--Mills on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is by definition the $(3+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 8 supercharges. Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\SU(2)\times \Spin(N_\RR)$. We consider a twisting homomorphism
\[\phi\colon \MU(L)\times \Spin(N_\RR)\rightarrow G_R=\SU(2)\times \Spin(N_\RR)\]
whose first component is $\MU(L)\rightarrow \SU(2)$ as before and the second component is the identity.

@@

\begin{thm}
The holomorphic twist of 4d $\cN=2$ super Yang--Mills on $M=\RR^4$ is perturbatively (with respect to the choice of twisting data $\alpha = \alpha_n$) is equivalent to the holomorphic BF theory on $M\cong\CC^2$ with the space of fields $T^*[-1] \map(M, (U\oplus \fg)/\fg)$. 
Moreover, the equivalence is $\U(2)$-equivariant.
\label{thm:4dholomorphictwist}
\end{thm}
\begin{proof}
4d $\cN=2$ super Yang--Mills theory is obtained by dimensionally reducing 6d $\cN=(1,0)$ super Yang--Mills theory. Under dimensional reduction the 6d fields from Section \ref{sec:6dholomorphictwist} decompose as follows:
\begin{align*}
A_{1, 0}&\rightsquigarrow A_{1, 0}, \Tilde{a} \\
A_{0, 1}&\rightsquigarrow A_{0, 1}, a \\
B&\rightsquigarrow B, b \\
\rho&\rightsquigarrow \rho, \Tilde{\chi} \\
\psi & \rightsquigarrow \psi, \varphi . \\
\end{align*}

@@

Next, we check that the equivalence respects  the gradings and the $\MU(2)$-action. 
Indeed, the equivalence given by Theorem \ref{thm:5dminimaltwist} eliminates fields $A_{1, 0}, \Tilde{a}, \rho, \chi, \Tilde{\chi}$ and hence the underlying local $L_\infty$ algebra after the twist becomes
\[
\xymatrix@R=0.5cm@C=0.5cm{
\ul{0} & \ul{1} & \ul{2} & \ul{3} & \\ 
\Omega^0(\CC^2; \gg)_c \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{B} \\
 & \Omega^0(\CC^2; \gg)_a \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{b} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{\xi^*} \\
  & \Omega^{2,0}(\CC^2 ; \gg)_{B^*} \ar[r] & \Omega^{2,1}(\CC^2 ; \gg)_{A_{0,1}^*} \ar[r] & \Omega^{2,2}(\CC^2 ; \gg)_{c^*} \\
 \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*}  \\
& \Omega^0(\CC^2 ; U)_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U)_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U)_{\varphi^*} \\
\Omega^{2,0}(\CC^2 ; U)_{\varphi} \ar[r] & \Omega^{2,1}(\CC^2 ; U)_{\psi^*} \ar[r] & \Omega^{2,2}(\CC^2 ; U)_{\phi^*}
}
\]
concentrated in cohomological degrees $0, \dots, 3$. These fields have the same degrees as in the holomorphic BF theory and the $L_\infty$ structure is obtained by the natural square zero extension of the dg Lie algebra in the first line by the remaining part of the diagram.
Finally, we observe that the twisted theory manifestly descends to a $\U(2)$-equivariant theory along the natural homomorphism $\MU(2) \to \U(2)$, and all identifications are $\U(2)$-equivariant. 
\end{proof}

@@

Let $\{s^1_+, s_+^2\}$ be a basis for $S_+^4$. 
We twist by a supercharge of the form
\begin{equation} 
\label{eq:4dHodgefamily}
Q_t = s_+^1 \otimes u \otimes \alpha_+ + t s_+^2 \otimes v \otimes \alpha_+
\end{equation}
where $t \in \CC$. 
When $t \ne 0$, this supercharge is of rank $(2,0)$. 
At $t = 0$ it reduces to the holomorphic supercharge from the previous section.

@@

\begin{prop}
Suppose $Q_t$ is the rank $(2,0)$ supercharge of \ref{eq:4dHodgefamily}.
The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 4d $\cN=2$ super Yang--Mills theory are
\begin{align*}
I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}a, b^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varphi, \phi^*) + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) \right) \\
I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac 14 t (\psi^*, \psi^*)
\end{align*}
\end{prop}
\begin{proof}
We first write down the fields and the functionals in $\Spin(4)$-notation.
The fields of $4d \cN=2$ decompose as:
\begin{itemize}
 \item $\gg$-valued bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(a \otimes \alpha_-^{\otimes 2} ,\Tilde{a} \otimes \alpha_+^{\otimes 2}) \in \Omega^0(\RR^4; (S^2_-)^{\otimes 2} \otimes \gg \oplus  (S^2_-)^{\otimes 2} \otimes \gg)$.
  \item $\gg$-valued fermions: a $W = W_+ \otimes S_+^2$-valued Dirac spinor $\lambda = (\lambda_+ \otimes \alpha_+, \lambda_-\otimes \alpha_-) \in \Omega^0(\RR^4; (S^4_+ \otimes W \oplus S^4_- \otimes W^*) \otimes \gg)$.
 \item $U$-valued bosons: a $W = W_+ \otimes S_+^2$-valued scalar field $\phi \otimes v \in \Omega^0(\RR^4; W_+ \otimes S_+^2 \otimes U)$.
 \item $U$-valued fermions: a Dirac spinor $\psi = (\psi_+ \otimes \alpha_- ,\psi_- \otimes \alpha_+) \in \Omega^0(\RR^4; (S^4_+ \otimes S_-^2 \oplus S^4_- \otimes S_+^2) \otimes U)$.
 \item a ghost $c \in \Omega^0(\RR^4 ; \gg)$.
\end{itemize}
The anti-fields decompose in an analogous way.

@@

\subsection{\texorpdfstring{$\cN = 2$}{N=2} Super Yang-Mills with Chiral Matter} \label{3d_2_section}
We'll begin with the minimal super Yang-Mills theory that admits non-trivial twists (if $\mc N=1$ there are no square-zero supercharges).  So, fix a gauge group $G$, and a representation $R$.  The 3d $\mc N=2$ super Yang-Mills theory arises by dimensional reduction from $\mc N=1$ super Yang-Mills theory on $\RR^4$ with an $R$-valued chiral multiplet.  We fix $W = \CC^2$ equipped with a nondegenerate symmetric bililear pairing.

The R-symmetry group is $\mr O(2)$, acting on $W$ by its defining representation.

This theory admits a unique twist:
\begin{itemize}
 \item A square zero supercharge $Q \ne 0 \in \Sigma$ has two invariant directions.  There is a twisting homomorphism $\phi \colon \MU(1) = \U(1)\hookrightarrow \mr O(2)$, so the twisted theory carries a $U(1)$-action.
\end{itemize}

We can describe the BRST field content of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_1_section} to representations of the group $\mr O(3)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and a scalar $\phi \in \Omega^0(\RR^3; \gg)$.
 \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^3 ; R \oplus R^*)$.
 \item $\gg$-valued fermions: $\lambda \otimes u \in \Omega^0(\RR^3 ; S \otimes \gg \otimes W)$.
 \item $R$-valued fermions: $(\psi_-,\psi_+) \in \Omega^0(\RR^3 ; S \otimes R \oplus \otimes S \otimes R^*)$.
\end{itemize}

\subsubsection{Minimal Twist}
A square-zero supercharge $Q$ has rank 1, i.e. $Q = q \otimes w$ for some $w \in W$.  There is an essentially trivial twisting homomorphism $\phi \colon \MU(1) = \U(1)\hookrightarrow \mr O(2)$.

As in Section \ref{sect:9dminimaltwist}, the data of $q_+$ is equivalent to the choice of a one-dimensional subspace $N_\RR\subset V_\RR$ and a complex structure on $V_\RR/N_\RR$ together with a complex half-density.  Note that in one dimension the choice of a complex half-density is equivalent to a choice of spin structure.

\begin{thm} \label{3d_minimal_twist_thm}
The minimal twist of 3d $\cN=2$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=2$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to mixed $BF$ theory for the Lie algebra $\fg$ coupled to the mixed $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$. Moreover this equivalence is $\mr U(1)$-equivariant.
\end{thm}

\begin{proof}
By Theorem \ref{4d_minimal_twist_thm} the twist of 4d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic Chern--Simons theory with the space of fields $T^*[-1]\map(L\times N, R / \fg)$. By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $T^*[-1]\map(L\times N_\RR, R/\fg)$ and this isomorphism is $\MU(1) = \mr U(1)$-equivariant.
\end{proof}

\subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang-Mills with Hypermultiplet Matter} \label{3d_4_section}
We will now consider 3d $\mc N=4$ theories, which arise by dimensional reduction from 4d $\mc N=2$ super Yang-Mills with gauge group $G$, coupled to a hypermultiplet valued in a symplectic representation $U$, or equivalently by dimensional reduction from 6d $\mc N=(1,0)$ super Yang-Mills coupled to a hypermultiplet.  The $R$-symmetry group is $G_R = \SO(4)$, acting on $W$ by its defining representation. \chris{or should it be $\spin(3;\RR)$?}

In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.  An element $Q \in S \otimes W$ gives rise to a map $S^* \to W$; $Q$ squares to zero if its image is totally isotropic.  The classification of orbits includes the rank of this map.
\begin{itemize}
 \item Rank 1.  In this case $Q$ is minimal, with 2 invariant directions.  Such supercharges come from the $\mc N=2$ supersymmetry algebra.  They admit a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
 \item Rank 2 $A$-twist.  Rank 2 supercharges are topological.  A rank 2 supercharge defines a Lagrangian subspace of $W$, and therefore a volume form.  There are two orbits for the $G_R = \SO(4)$ action on the space of volume forms, which we refer to as the $A$-twist and the $B$-twist.  The $A$-twist arises by dimensional reduction from the rank $(2,0)$ twist in 4d.  It admits a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
 \item Rank 2 $B$-twist.  The other topological orbit arises by dimensional reduction from the rank $(1,1)$ twist in 4d.  It admits a twisting homomorphism $\phi \colon \spin(3;\RR) \iso \SU(2) \to \SO(4)$. 
\end{itemize}

We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\mr O(3)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and three scalar fields $(\phi_1,\phi_2,\phi_3) \in \Omega^0(\RR^3; \gg \oplus \gg \oplus \gg)$.
 \item $U$-valued bosons: a $W$-valued scalar field $(\phi \otimes v) \in \Omega^0(\RR^3; W \otimes U)$.
 \item $\gg$-valued fermions: a pair of $W$-valued spinors $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes \gg \otimes (W \oplus W))$.
 \item $U$-valued fermions:  a pair of spinors $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
\end{itemize}

\subsubsection{Minimal Twist}
The 3d $\cN=4$ super Yang--Mills viewed as a $\cN=2$ supersymmetric theory coincides with the 3d $\cN=2$ super Yang--Mills with matter valued in the representation $R = U \oplus \gg$. From Theorem \ref{3d_minimal_twist_thm} we obtain the following statement.

\begin{theorem} \label{3d_4_minimal_twist_thm}
The minimal twist of 3d $\cN=4$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(\CC \times \RR_{\mr{dR}}, T^*[1](U\ham \gg))$. Moreover, the equivalence is $\U(1)$-equivariant.
\end{theorem}

\subsubsection{Topological A Twist}
Let $L=\CC$ equipped with a Hermitian structure and a complex half density, $N_\RR=\RR$ equipped with a Euclidean structure and $N=N_\RR\otimes_\RR\CC$ its complexification. Consider the 4-dimensional spacetime $V_\RR=L\times N$. Under the projection $\Re\colon N\rightarrow N_\RR$ the family $Q_t$ of 4-dimensional square-zero supercharges given by \eqref{eq:4dHodgefamily} dimensionally reduces to a family of 3-dimensional square-zero supercharges which at $t\neq 0$ are topological at and $t=0$ have 2 invariant directions. Since they admit a compatible $\ZZ$-grading, at $t=0$ we obtain the holomorphic twist and at $t\neq 0$ we obtain the topological B twist. Therefore, from Theorem \ref{thm:4dDonaldsontwist} we obtain the following statement.

\begin{thm}
The twist of 3d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\mr{Map}(\CC \times \RR_{\mr{dR}}, (U\ham \gg)_{\mr{Hod}})$. Moreover, this equivalence is $\U(1)$-equivariant.
\label{3d_4_A_twist_thm}
\end{thm}

\begin{cor}
The topological $A$ twist of 3d $\cN=4$ super Yang--Mills is perturbatively trivial.
\end{cor}

>>>>

The dimensional reduction of 8d $\cN=1$ super Yang--Mills on $L\times N$ alond $\Re\colon N\rightarrow N_\RR$ is by definition the $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 16 supercharges. Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\U(1)\times \Spin(N_\RR)$. We consider the grading $\alpha\colon \U(1)\rightarrow G_\RR$ given by the embedding into the first copy of $\U(1)$ and a twisting homomorphism
\[\phi\colon \MU(L)\times \Spin(N_\RR)\xrightarrow{\det^{1/2}\times \id} G_R=\U(1)\times \Spin(N_\RR).\]

@@

The dimensional reduction of 6d super Yang--Mills on $L\times N$ alond $\Re\colon N\rightarrow N_\RR$ is by definition the $(3+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 8 supercharges. Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\SU(2)\times \Spin(N_\RR)$. We consider a twisting homomorphism
\[\phi\colon \MU(L)\times \Spin(N_\RR)\rightarrow G_R=\SU(2)\times \Spin(N_\RR)\]
whose first component is $\MU(L)\rightarrow \SU(2)$ as before and the second component is the identity.

@@

\begin{thm}
The holomorphic twist of 4d $\cN=2$ super Yang--Mills on $M=\RR^4$ is perturbatively (with respect to the choice of twisting data $\alpha = \alpha_n$) is equivalent to the holomorphic BF theory on $M\cong\CC^2$ with the space of fields $T^*[-1] \map(M, (U[2n] \oplus \fg[-4n+2])/\fg)$. 
Moreover, the equivalence is $\U(2)$-equivariant.
\label{thm:4dholomorphictwist}
\end{thm}
\begin{proof}
4d $\cN=2$ super Yang--Mills theory is obtained by dimensionally reducing 6d $\cN=(1,0)$ super Yang--Mills theory. Under dimensional reduction the 6d fields from Section \ref{sec:6dholomorphictwist} decompose as follows:
\begin{align*}
A_{1, 0}&\rightsquigarrow A_{1, 0}, \Tilde{a} \\
A_{0, 1}&\rightsquigarrow A_{0, 1}, a \\
B&\rightsquigarrow B, b \\
\rho&\rightsquigarrow \rho, \Tilde{\chi} \\
\psi & \rightsquigarrow \psi, \varphi . \\
\end{align*}

@@

Next, we check that the equivalence respects  the gradings and the $\MU(2)$-action. 
Indeed, the equivalence given by Theorem \ref{thm:5dminimaltwist} eliminates fields $A_{1, 0}, \Tilde{a}, \rho, \chi, \Tilde{\chi}$ and hence the underlying local $L_\infty$ algebra after the twist becomes
\[
\xymatrix@R=0.5cm@C=0.5cm{
\ul{0} & \ul{1} & \ul{2} & \ul{3} & \\ 
\Omega^0(\CC^2; \gg)_c \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{B} \\
  & \Omega^{2,0}(\CC^2 ; \gg)_{B^*} \ar[r] & \Omega^{2,1}(\CC^2 ; \gg)_{A_{0,1}^*} \ar[r] & \Omega^{2,2}(\CC^2 ; \gg)_{c^*} \\
  }
\]

\[
\xymatrix@R=0.5cm@C=0.5cm{
\ul{-4n+2} & \ul{-4n+3} & \ul{-4n+4} & \cdots & \ul{4n-1} & \ul{4n} & \ul{4n+1} \\ 
 &&&& \Omega^0(\CC^2; \gg)_a \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{b} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{\xi^*} \\
 \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*}  \\
}
\]

\[
\xymatrix@R=0.5cm@C=0.5cm{
\ul{-2n+1} & \ul{-2n+2} & \ul{-2n+3} & \cdots & \ul{2n} & \ul{2n+1} & \ul{2n+2} \\ 
\Omega^0(\CC^2 ; U)_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U)_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U)_{\varphi^*} \\
& & & & \Omega^{2,0}(\CC^2 ; U)_{\varphi} \ar[r] & \Omega^{2,1}(\CC^2 ; U)_{\psi^*} \ar[r] & \Omega^{2,2}(\CC^2 ; U)_{\phi^*}
}
\]
These fields have the same degrees as in the holomorphic BF theory and the $L_\infty$ structure is obtained by the natural square zero extension of the dg Lie algebra in the first line by the remaining part of the diagram.
Finally, we observe that the twisted theory manifestly descends to a $\U(2)$-equivariant theory along the natural homomorphism $\MU(2) \to \U(2)$, and all identifications are $\U(2)$-equivariant. 
\end{proof}

@@

Let $\{s^1_+, s_+^2\}$ be a basis for $S_+^4$. 
We twist by a supercharge of the form
\[
Q_t = s_+^1 \otimes u \otimes \alpha_+ + t s_+^2 \otimes v \otimes \alpha_+
\]
where $t \in \CC$. 
When $t \ne 0$, this supercharge is of rank $(2,0)$. 
At $t = 0$ it reduces to the holomorphic supercharge from the previous section.

@@

\begin{prop}
Suppose $Q_t$ is the rank $(2,0)$ supercharge as above.
The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 4d $\cN=2$ super Yang--Mills theory are
\begin{align*}
I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}a, b^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varphi, \phi^*) + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) \right) \\
I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac 14 t (\psi^*, \psi^*)
\end{align*}
\end{prop}
\begin{proof}
We first write down the fields and the functionals in $\Spin(4)$-notation.
The fields of $4d \cN=2$ decompose as:
\begin{itemize}
 \item $\gg$-valued bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(a \otimes \alpha_-^{\otimes 2} ,\Tilde{a} \otimes \alpha_+^{\otimes 2}) \in \Omega^0(\RR^4; (S^2_-)^{\otimes 2} \otimes \gg \oplus  (S^2_-)^{\otimes 2} \otimes \gg)$.
  \item $\gg$-valued fermions: a $W = W_+ \otimes S_+^2$-valued Dirac spinor $\lambda = (\lambda_+ \otimes \alpha_+, \lambda_-\otimes \alpha_-) \in \Omega^0(\RR^4; (S^4_+ \otimes W \oplus S^4_- \otimes W^*) \otimes \gg)$.
 \item $U$-valued bosons: a $W = W_+ \otimes S_+^2$-valued scalar field $\phi \otimes v \in \Omega^0(\RR^4; W_+ \otimes S_+^2 \otimes U)$.
 \item $U$-valued fermions: a Dirac spinor $\psi = (\psi_+ \otimes \alpha_- ,\psi_- \otimes \alpha_+) \in \Omega^0(\RR^4; (S^4_+ \otimes S_-^2 \oplus S^4_- \otimes S_+^2) \otimes U)$.
 \item a ghost $c \in \Omega^0(\RR^4 ; \gg)$.
\end{itemize}
The anti-fields decompose in an analogous way.

@@

\subsection{\texorpdfstring{$\cN = 2$}{N=2} Super Yang-Mills with Chiral Matter} \label{3d_2_section}
We'll begin with the minimal super Yang-Mills theory that admits non-trivial twists (if $\mc N=1$ there are no square-zero supercharges).  So, fix a gauge group $G$, and a representation $R$.  The 3d $\mc N=2$ super Yang-Mills theory arises by dimensional reduction from $\mc N=1$ super Yang-Mills theory on $\RR^4$ with an $R$-valued chiral multiplet.

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_1_section} to representations of the group $\mr O(3)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and a scalar $\phi \in \Omega^0(\RR^3; \gg)$.
 \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^3 ; R \oplus R^*)$.
 \item $\gg$-valued fermions: $\lambda \otimes u \in \Omega^0(\RR^3 ; S \otimes \gg \otimes W)$.
 \item $R$-valued fermions: $(\psi_-,\psi_+) \in \Omega^0(\RR^3 ; S \otimes R \oplus \otimes S \otimes R^*)$.
\end{itemize}

\vspace{-10pt}
\paragraph{Twisting data:}
In the $\mc N=2$ supersymmetry algebra there is a unique non-trivial orbit of square-zero supercharges, with rank one. \chris{todo, say something about $\ZZ$-gradings and twisting homomorphisms.}

\begin{thm} \label{3d_minimal_twist_thm}
The minimal twist of 3d $\cN=2$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=2$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to mixed $BF$ theory for the Lie algebra $\fg$ coupled to the mixed $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$. 
\end{thm}

\begin{proof}
This follows by dimensionally reducing the holomorphic twist of 4d $\mc N=1$ super Yang-Mills.  That is, we start with the result from Theorem \ref{4d_minimal_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to turn one of the complex directions into a real de Rham direction.
\end{proof}

\subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang-Mills with Hypermultiplet Matter} \label{3d_4_section}
We will now consider 3d $\mc N=4$ theories, which arise by dimensional reduction from 4d $\mc N=2$ super Yang-Mills with gauge group $G$, coupled to a hypermultiplet valued in a symplectic representation $U$, or equivalently by dimensional reduction from 6d $\mc N=(1,0)$ super Yang-Mills coupled to a hypermultiplet.

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\mr O(3)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and three scalar fields $(\phi_1,\phi_2,\phi_3) \in \Omega^0(\RR^3; \gg \oplus \gg \oplus \gg)$.
 \item $U$-valued bosons: a $W$-valued scalar field $(\phi \otimes v) \in \Omega^0(\RR^3; W \otimes U)$.
 \item $\gg$-valued fermions: a pair of $W$-valued spinors $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes \gg \otimes (W \oplus W))$.
 \item $U$-valued fermions:  a pair of spinors $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
\end{itemize}

\vspace{-10pt}
\paragraph{Twisting data:}
In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.  In addition to rank one square-zero supercharges, which sit inside an $\mc N=2$ subalgebra, there are two possible classes of rank two square-zero supercharges.  The corresponding twisted theories are obtained by dimensionally reducing the 4d $\mc N=2$ theory twisted by a rank $(1,1)$, or a rank $(2,0)$ square-zero supercharge.  Let's first discuss the rank 1 twist, and its deformation to a perturbatively trivial rank 2 twist.

\begin{theorem} \label{3d_4_holo_A_twist_thm}
The minimal twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(\CC \times \RR_{\mr{dR}}, T^*[1](U\ham \gg))$. The deformation of this theory to the rank 2 A-twist corresponds to deforming this theory to the 1-parameter family $\mr{Map}(\CC \times \RR_{\mr{dR}}, (U\ham \gg)_{\mr{Hod}})$.
\end{theorem}

\begin{proof}
To prove this, we start with the one-parameter family of 4d twisted theories which we computed Theorem \ref{4d_Donaldson_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to reduce to a one-parameter family of 3d twisted theories.
\end{proof}

\begin{theorem} \label{3d_2_B_twist_thm}
The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(\RR^3_{\mr{dR}}, U\ham \gg)$.  This theory is generally only $\ZZ/2\ZZ$-graded.
\end{theorem}

\begin{proof}
Again, we prove this by dimensional reduction from a 4d $\mc N=2$ twisted theory, in this case the rank $(1,1)$ twist from Theorem \ref{4d_11_twist_thm}, by applying Proposition \ref{CS_diml_red_prop}.
\end{proof}

\subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang-Mills Theory} \label{3d_8_section}
Finally, let's consider maximal super Yang-Mills theory with gauge group $G$ in dimension 3, with $\mc N=8$ supersymmetry.  This is the theory obtained by compactifying $\mc N=(1,0)$ super Yang-Mills on $\RR^{10}$ down to $\RR^3$.

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\mr O(3)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item Bosons: $A \in \Omega^1(\RR^3; \gg)$, and seven scalar fields $\phi_i \in \Omega^0(\RR^3; \gg)$.
 \item Fermions: eight spinor fields $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$.
\end{itemize}

\vspace{-10pt}
\paragraph{Twisting data:}
The classes of square-zero supercharge in the 3d $\mc N=8$ supersymmetry algebra are categorized in the same way as in the $\mc N=4$ supersymmetry algebra.  There are minimal twisting supercharges of rank 1, and two classes of topological twisting supercharges of rank 2, which we refer to as the A-twist (obtained from a rank $(2,0), (2,1)$ or generic $(2,2)$ supercharge in $4d \mc N=4$), and the B-twist (obtained from a rank $(1,1)$ or special rank $(2,2)$ supercharge in 4d $\mc N=4$).  The twisted theories can be calculated either by dimensional reduction -- by applying Proposition \ref{CS_diml_red_prop} to the theories from Section \ref{4d_4_section}, or from the 3d $\mc N=4$ twists by considering the representation $U = T^*\gg$.

\begin{theorem} 
The minimal twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Dol}})$. The deformation of this theory to the rank 2 A-twist corresponds to deforming this theory to the 1-parameter family $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Hod}})$.
\end{theorem}

\begin{theorem} 
The rank $2$ B-twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$. 
\end{theorem}
